%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 11pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{hyperref}
\usepackage{xcolor}

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Dekel Pilli} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
\moveleft.5\hoffset\centerline{Melbourne, 3000}
\moveleft.5\hoffset\centerline{Ph: 0401 995 442; E: dekelpilli@gmail.com}
%\moveleft.5\hoffset\centerline{dekelpilli@gmail.com}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNOLOGY \\ SKILLS} 
\begin{itemize}

\item \textbf{Proficient Programming Languages:} Clojure, Java, Python, Terraform.
\item \textbf{Other Languages Used:} Rust, C, C\#, AngularJS, Perl, PHP
\item \textbf{Technologies Used:}
\begin{itemize}
\item \textbf{SQL:} PostgreSQL, SQL Server, MySQL, MySQL Aurora
\item \textbf{noSQL/KV:} ScyllaDB, DynamoDB, Redis, RocksDB
\item \textbf{Frameworks:}  Spring (Java), Tokio (Rust)
\item \textbf{Messaging:} Redis, SQS, ActiveMQ, SNS, Kafka
\item \textbf{Storage:} SFTP, S3, Minio
\item \textbf{CI:} Jenkins, Github Actions, Gitlab CI
\item \textbf{Environment management \& runtimes:} Docker, Nomad, Consul, various AWS tools (ECS Fargate, SSM, Lambda, Step Functions, Glue, EC2), Tomcat
\item Comfortable working on Linux, OSX, and Windows operating systems. 
\end{itemize}
\end{itemize}
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{EXPERIENCE}
\textbf{Software Engineer} \hfill September 2020 - Present \\
{\sl Core0/Kakku}
\vspace{15pt}\\
%TODO

\textbf{Software Engineer} \hfill August 2019 - September 2020 \\
{\sl Littlepay}

\begin{itemize}
\item Integration with several acquirers, mainly using ISO8583, and PCI-compliant handling of cardholder data.
\item Analytics platform ownership, including design, development, production deployments, and support.
\item Process and tool improvement through POCs and implementation thereafter.

\end{itemize}


\textbf{Key Achievements}

\begin{itemize}
\item Significantly improved performance and stability of the analytics platform.
\item Several succesful and timely acquirer integrations.
\item General technlogical improvement across the stack; uplifting, deprecating and replacing legacy systems thourghout the product streams.

\end{itemize}


\textbf{Graduate Developer} \hfill May 2018 - August 2019 \\
{\sl Intelematics Australia}
\vspace{15pt}\\
\textbf{Key Responsibilities}

\begin{itemize}
\item Gained experience with a large variety of applications and development styles, ranging from legacy systems to new cloud-based applications.
\item Database refactor leading to the removal of over a terrabyte of indexes and hundreds of tables and stored procedures. This also resulted in significantly improved performance for end users.
\item Actively challenged myself to work with new technologies, including CI with Jenkins and Spinnaker, and Infrastructure as Code with Terraform.

\end{itemize} 

\textbf{Key Achievements}

\begin{itemize}

\item Was a major contributor to a cloud-hosted webapp that integrated a variety of AWS services to provide a set of REST endpoints that significantly outperformed their on-premises, SQL-based equivalents.
\item Single-handedly designed and implemented a major business logic refactor in a legacy system, satisfying all stakeholders and substantially improving the quality of our data. 
\item Subject matter expert for several microservices.


\end{itemize}


\textbf{Software Engineer} \hfill February 2018 - October 2018 \\
{\sl Online Hate Prevention Institute}
\vspace{15pt}\\
Casual position as a software engineer. The position was offered to me by the Institute CEO after completion of the University capstone project with them in 2017. The work is on a different project to the one from University and is focused on extending the functionality and improving the code quality of an existing system using Spring MVC.




%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%---------------------------------------------------------------------------------------- 

\section{EDUCATION}

\begin{itemize}

\item Graduated from  Monash University with a Bachelor of Software Engineering.
\item Completed year 12 VCE at McKinnon Secondary College, having studied Specialist  Mathematics, Information Technology Applications, Physics, English, Mathematical Methods, and Hebrew.

\end{itemize}

%----------------------------------------------------------------------------------------
%	OTHER JOBS AND VOLUNTEERING SECTION
%----------------------------------------------------------------------------------------

\section{OTHER JOBS} 

\begin{itemize} \itemsep -11pt

\item EA Sports FIFA, {\sl Managing Editor} \hfill 2014 - 2017\\
\item Monash Computer Games Boot Camp, {\sl Volunteer} \hfill 2016 \\
\item EA Sports FIFA, {\sl Data Reviewer} \hfill 2013 - 2014 \\
 
\end{itemize}


%----------------------------------------------------------------------------------------
%	PORTFOLIO SECTION
%----------------------------------------------------------------------------------------


\section{PORTFOLIO} 

My works from third year University onwards, including personal projects and open source contributions, are available \underline{\color{blue}{\href{https://github.com/dekelpilli?tab=repositories}{here}}}.



%----------------------------------------------------------------------------------------


\section{ELIGIBILITY \\ \& REFERENCES} 

I am an Australian citizen, and my references are available upon request.

\end{resume}
\end{document}